Tools for identifying unexpectely low microfossil count sums

### 2019-05-02 Rmd/count_check_MS.Rmd
countChecker -> countSum package

All analyses were done in R version `r getRversion()` [@R] and used the packages extraDistr version `r packageVersion("extraDistr")` [@extraDistr], numbers version `r packageVersion("numbers")` [@numbers], and countChecker `r packageVersion("countChecker")` [@countChecker].
Code to replicate all the analyses shown above is archived at [https://github.com/richardjtelford/count.check.ms](https://github.com/richardjtelford/count.check.ms).

@@

The `r last_chance_summ$nsamples` chironomid head capsule assemblage dataset from Last Chance Lake [@Axford2017] also includes both the count sums and the percentage of each taxa.
The percentages are given to two decimal places: to account for rounding errors, the countChecker package uses the smallest and largest values consistent with the reported percentage.
With the minimum percent method the estimated count sums are, within error, either identical to the reported count sum or twice as much (Fig. \@ref(fig:last-chance-plot)).
With the direct search method, the estimated count sums are all exactly twice the reported count sum.
The factor of two difference is because all the counts include half head capsules (but only sometimes is the rarest taxon represented by a half head capsule).
Reporting half microfossils is common for several microfossil groups, including chironomids and pollen (especially for bisaccate conifers); occasionally other fractions are reported.
Half counts make the estimated count too high by a factor of two, so do not risk incorrectly flagging count sums as being too small.
The direct search method is more precise than the minimum percent method as the rounding error is relatively smaller on the larger percent values the method uses.

>>>>

All analyses were done in R version `r getRversion()` [@R] and used the packages extraDistr version `r packageVersion("extraDistr")` [@extraDistr], numbers version `r packageVersion("numbers")` [@numbers], and countSum `r packageVersion("countSum")` [@countSum].
Code to replicate all the analyses shown above is archived at [https://github.com/richardjtelford/count.check.ms](https://github.com/richardjtelford/count.check.ms).

@@

The `r last_chance_summ$nsamples` chironomid head capsule assemblage dataset from Last Chance Lake [@Axford2017] also includes both the count sums and the percentage of each taxa.
The percentages are given to two decimal places: to account for rounding errors, the countSum package uses the smallest and largest values consistent with the reported percentage.
With the minimum percent method the estimated count sums are, within error, either identical to the reported count sum or twice as much (Fig. \@ref(fig:last-chance-plot)).
With the direct search method, the estimated count sums are all exactly twice the reported count sum.
The factor of two difference is because all the counts include half head capsules (but only sometimes is the rarest taxon represented by a half head capsule).
Reporting half microfossils is common for several microfossil groups, including chironomids and pollen (especially for bisaccate conifers); occasionally other fractions are reported.
Half counts make the estimated count too high by a factor of two, so do not risk incorrectly flagging count sums as being too small.
The direct search method is more precise than the minimum percent method as the rounding error is relatively smaller on the larger percent values the method uses.
